---
title: "Specification curve"
output:
  html_document:
    number_sections: yes
  pdf_document:
    number_sections: yes

---


Possible arguments to vary over:

* Covariates y/n
* Weighted y/n
* Standard errors clustering (on politician vs at level of randomization)
* NOT IMPLEMENTED: Logit/LPM
* Dropping cases with missing Ps versus imputing using the individual study PAP procedures
* Mexico posteriors minus priors versus Q-only approach
* Ug1 good/bad news Ug1 PAP versus revised coding
* Ug2 chairs only y/n
* Ug2 contested elections y/n
* Ug2 LC3 included y/n ??
* BF: recoding the m3=0/m1=1 as m1=0 cases y/n

```{r, echo=FALSE}
standalone <- FALSE #whether running this file independently or rendering in main replication file
```


```{r, echo=FALSE, eval=standalone, warning=FALSE, message=FALSE}
library(tidyr); library(plyr); library(dplyr); library(lfe); library(ggplot2);library(gridExtra)
library(xtable)

source("0a_functions_main.R")

export_to_book <- TRUE
book_dir <- "11 Book/4 Manuscript drafts/201804 For Copyediting/files"
load_specification_matrices <- TRUE #if FALSE will generate matrices for specification curve from scratch (time intensive)
```

# Function to generate all specification results

```{r}
run_spec <- function(leave_out,
                     bf_m1_recode,   # if TRUE, codes voting for incumbent as 0 when m3==0 and m1==1
                     ug1_m10_recode, # if TRUE, uses diff btw Q and P aggregated
                     mex_m10_recode, # if TRUE, uses post - prior(control post) diff
                     NA_P_recode,    
                     depvar,
                     news,
                     # model,
                     cl_pol,
                     weights,
                     cov,
                     with_N,
                     contested_seats,
                     exclude_councilors,
                     exclude_redistrict,
                     exclude_switch
                     ){
  
  dat <- madat
  #leave_out
  if(leave_out!="none") dat <- dat[madat$ctry != leave_out,]
    
  # NA_P_coding
  if(NA_P_recode){
    missingP <- which(((is.na(dat$mpprior) | 
                        is.na(dat$mpdistrictalign_perc) | 
                        is.na(dat$mpmoneyalign_perc)) & dat$ctry == "ug1") | 
                        is.na(dat$P))
    dat$N_good[missingP] <- NA
    dat$m9[dat$ctry=="mex"] <- dat$prior_i4[dat$ctry=="mex"] #non imputed values
  }
  
  # bf_m1_coding
  #m3==0 in Burkina Faso means unlikely to vote or definitely not voting.
  if(bf_m1_recode) dat$m1[dat$m1==1 & dat$m3==0 & dat$ctry == "bf"] <- 0

  # ug1_m10_recode
  if(ug1_m10_recode){
    dat$N_good[dat$ctry=="ug1"] <- 1*(dat$N_alt[dat$ctry=="ug1"]>0)
  }

  # mex_m10_coding
  if(mex_m10_recode){
    dat$mex_news <- dat$m9 - dat$posterior_incumbent43
    table(dat$posterior_incumbent43[dat$ctry=="mex" & dat$posterior_incumbent43==dat$m9])
    dat$mex_news <- case_when(dat$mex_news>0 ~ 1,
                                dat$mex_news==0 & dat$posterior_incumbent43 < 0 ~ 1,
                                dat$mex_news==0 & dat$posterior_incumbent43 > 0 ~ 0,
                                dat$mex_news<0 ~ 0)
    #tie-breaking when news==0 & posterior==0 & prior==0? (113 obs missing news coding)
    dat$N_good[dat$ctry=="mex"] <- dat$mex_news[dat$ctry == "mex"]
  }

  #estimates function return dat
  if(cov=="") cov <- NULL
  
  good <- case_when(news == "good" ~ TRUE,
                    news == "bad" ~ FALSE)
  
  if(is.na(good)) good <- NULL
  
  if(exclude_redistrict){
    dat <- dat[is.na(dat$lc5.councillor.redistricted2016)|dat$lc5.councillor.redistricted2016=="TRUE",]
  }
  
  if(exclude_switch){
    dat <- dat[is.na(dat$lc5.chair.party.switch)|dat$lc5.chair.party.switch==0,]
    dat <- dat[is.na(dat$lc5.councillor.party.switch)|dat$lc5.councillor.party.switch==0,]
  }
  
  if(cl_pol){
    dat$cl <- dat$cl_pol    
    est <- estimates(dat = dat,
                      depvar = depvar, exclude_councilors = exclude_councilors,
                      cov = cov, weights = weights,
                      good = good, with_N = with_N, contested_seats = contested_seats, 
                      country = NULL)
  }else{
      
      est <- estimates(dat = dat,
                      depvar = depvar, exclude_councilors = exclude_councilors, 
                      cov = cov, weights = weights,
                      good = good, with_N = with_N, contested_seats = contested_seats, 
                      country = NULL)
  }
  
  return(est)
}

```

# Create grid of all specifications

```{r}
args <- list(
  leave_out = c("none", "ben", "brz", "bf", "mex", "ug1", "ug2"),
  bf_m1_recode = c(TRUE, FALSE),
  ug1_m10_recode = c(TRUE, FALSE),
  mex_m10_recode = c(TRUE, FALSE),
  NA_P_recode = c(TRUE, FALSE),
  depvar = c("m1", "m3"),
  news = c("good", "bad"),# "overall"),
  # model = c("logit", "lpm"),
  cl_pol = c(TRUE, FALSE),
  weights = c(TRUE, FALSE),
  cov = c("", "m14i+m17i+m18i+m20i+m21i+m22i+m24i+m26i+m27i"),
  with_N = c(TRUE, FALSE),
  contested_seats = c(TRUE, FALSE),
  exclude_councilors = c(TRUE, FALSE),
  exclude_redistrict = c(TRUE, FALSE),
  exclude_switch = c(TRUE, FALSE)
  )

args_m <- expand.grid(args, stringsAsFactors = FALSE)
```

# Get rid of redundant/non-sensical specifications
```{r}
args_m <- args_m %>% 
  filter(!(leave_out == "ug2" & (contested_seats == TRUE | exclude_councilors == TRUE | 
                                   exclude_redistrict == TRUE | exclude_switch == TRUE))) %>% 
  filter(!(leave_out == "bf" & bf_m1_recode == TRUE)) %>%
  filter(!(leave_out == "mex" & mex_m10_recode == TRUE)) %>%
  filter(!(leave_out == "ug1" & ug1_m10_recode == TRUE))
```

#Apply function and return est and p-values.
```{r}

  #REVIEW: politician-level key var
  # mexsurdat - municipality
  # ug1 - candidateid
  # ug2 - district_lower
  # brz- muni
  # ben - commune 
  # bf - commune

  madat <- pool_studies(
    add_vars= c("nij", "Q_alt", "N_alt",
                "posterior_incumbent43", #posterior on incumbent with missing values replaced by 0
                "prior_i4", #prior without imputation (with imputation imported as m9)
                "mppriorug", "mpdistrictalign_perc", "mpmoneyalign_perc", 
                "municipality", "muni", "commune", "district_lower", "candidateid"),           
    dir = "data/temp")

  madat$cl_pol <- case_when(madat$ctry == "ben" ~ as.character(paste0(madat$ctry, madat$commune)),
                          madat$ctry == "bf" ~ as.character(paste0(madat$ctry, madat$commune)),
                          madat$ctry == "brz" ~ as.character(paste0(madat$ctry, madat$muni)),
                          madat$ctry == "mex" ~ as.character(paste0(madat$ctry, madat$municipality)),
                          madat$ctry == "ug1" ~ as.character(paste0(madat$ctry, madat$candidateid)),
                          madat$ctry == "ug2" ~ as.character(paste0(madat$ctry, madat$district_lower)))

  madat$m1[is.na(madat$m1) & madat$m3==0] <- 0
```

```{r, echo=FALSE}

specs_output <- function(args_matrix){
  tab <- t(sapply(1:nrow(args_matrix), function(i) get_ate(args_matrix[i,])))
  tab <- as.data.frame(tab)
  colnames(tab) <- c("ate","p")
  tab
  }

get_ate <- function(x){
  args <- as.list(x)
  fit <- do.call(run_spec, args = args)
  ate <- summary(fit)$coefficients["treat","Estimate"]
  pval <- summary(fit)$coefficients["treat","Pr(>|t|)"]
  return(c(ate, pval))
}

prep_graph <- function(mat, args){
  df <- as.data.frame(apply(args, 2, paste0), stringsAsFactors = FALSE)
  df$ate <- mat$ate
  df$p <- mat$p
  df <- df %>% gather(variable, value, -ate, -p)
  df <- df %>% unite(categ, c("variable", "value"), sep = "_")
  df$sign_95 <- (df$p<0.05)
  # df <- df %>% arrange(ate)
  df <- df %>% filter(!categ %in% c("depvar_m1","depvar_m3"))
  
  df$categ <- with(df, case_when(
                        categ == "with_N_FALSE" ~ "Nij included as covariate",
                        categ == "with_N_ TRUE" ~ "Nij not included as covariate",
                        categ == "cov_m14i+m17i+m18i+m20i+m21i+m22i+m24i+m26i+m27i" ~ "Adjusted",
                        categ == "cov_" ~ "Unadjusted",
                        categ == "news_good" ~ "ALL SPECIFICATIONS",
                        categ == "news_bad" ~ "ALL SPECIFICATIONS",
                        categ == "weights_FALSE" ~ "Weight individuals equally",
                        categ == "weights_ TRUE" ~ "Weight studies equally",
                        categ == "cl_pol_FALSE" ~ "Cluster: level of assignment",
                        categ == "cl_pol_ TRUE" ~ "Cluster: politician",
                        categ == "NA_P_recode_FALSE" ~ "P recoded when missing",
                        categ == "NA_P_recode_ TRUE" ~ "P dropped when missing",
                        categ == "mex_m10_recode_FALSE" ~ "Mexico: News coded using Q",
                        categ == "mex_m10_recode_ TRUE" ~ "Mexico: News coded using posterior-prior",
                        categ == "ug1_m10_recode_FALSE" ~ "Uganda 1: News!=0 when P=Q", 
                        categ == "ug1_m10_recode_ TRUE" ~ "Uganda 1: News=0 when P=Q",
                        categ == "bf_m1_recode_FALSE" ~ "Burkina: M1 not recoded",
                        categ == "bf_m1_recode_ TRUE" ~ "Burkina: M1=0 when M3=0",
                        categ == "exclude_councilors_FALSE" ~ "Uganda 2: include LCV councilors",
                        categ == "exclude_councilors_ TRUE" ~ "Uganda 2: exclude LCV councilors",
                        categ == "exclude_redistrict_FALSE" ~ "Uganda 2: include redistricted councilors",
                        categ == "exclude_redistrict_ TRUE" ~ "Uganda 2: exclude redistricted councilors",
                        categ == "exclude_switch_FALSE" ~ "Uganda 2: include party switches",
                        categ == "exclude_switch_ TRUE" ~ "Uganda 2: exclude party switches",
                        categ == "contested_seats_FALSE" ~ "Uganda 2: Include uncontested seats",
                        categ == "contested_seats_ TRUE" ~ "Uganda 2: Exclude uncontested seats",
                        categ == "leave_out_ug2" ~ "Leave out: Uganda 2",
                        categ == "leave_out_ug1" ~ "Leave out: Uganda 1",
                        categ == "leave_out_mex" ~ "Leave out: Mexico",
                        categ == "leave_out_bf" ~ "Leave out: Burkina Faso",
                        categ == "leave_out_brz" ~ "Leave out: Brazil",
                        categ == "leave_out_ben" ~ "Leave out: Benin",
                        categ == "leave_out_none" ~ "Leave out: Include all"))
  df$categ <- factor(df$categ,
                     levels = c(unique(df$categ)[1:13], unique(df$categ)[25:32], setdiff(unique(df$categ)[14:24], "ALL SPECIFICATIONS"), "ALL SPECIFICATIONS"))
  df
}



plot_spec_ate <- function(mat, args, title=""){
  df <- prep_graph(mat, args)
  df$term <- df$categ
  df$y_ind <- as.numeric(df$categ)
  # df$sign_95 <- factor(df$sign_95, levels = c(TRUE, FALSE))
  p <- ggplot(data=df) +
    geom_point(aes(y = categ, x = ate, color=sign_95, alpha = sign_95), shape = 3, size = .5) +
    theme_bw() + 
    scale_alpha_discrete(range=c(.1, .6)) +
    scale_color_manual(values=c("grey", "black")) +
    theme(legend.position="none") + 
    labs(title = title) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())
  
  # g <- p %>% add_brackets(brackets)
  # grid.arrange(p)
  return(p)  
}

# brackets <- list(c("", levels(df$categ)[28], levels(df$categ)[28]),
#                  c("", levels(df$categ)[26:27]),
#                  c("", levels(df$categ)[24:25]),
#                  c("", levels(df$categ)[22:23]),
#                  c("", levels(df$categ)[20:21]),
#                  c("", levels(df$categ)[18:19]),
#                  c("", levels(df$categ)[16:17]),
#                  c("", levels(df$categ)[14:15]),
#                  c("", levels(df$categ)[12:13]),
#                  c("", levels(df$categ)[8:9]),
#                  c("", levels(df$categ)[c(1,7)]))

# #Credit: https://stackoverflow.com/questions/6178763/how-to-add-braces-to-a-graph/9310002#9310002
# # Function to create curly braces
# # x, y position where to put the braces
# # range is the widht
# # position: 1 vertical, 2 horizontal
# # direction: 1 left/down, 2 right/up
# CurlyBraces <- function(x, y, range, pos = 1, direction = 1 ) {
# 
#     a=c(1,2,3,48,50)    # set flexion point for spline
#     b=c(0,.2,.28,.7,.8) # set depth for spline flexion point
# 
#     curve = spline(a, b, n = 50, method = "natural")$y / 2 
# 
#     curve = c(curve,rev(curve))
# 
#     a_sequence = rep(x,100)
#     b_sequence = seq(y-range/2,y+range/2,length=100)  
# 
#     # direction
#     if(direction==1)
#     a_sequence = a_sequence+curve
#     if(direction==2)
#     a_sequence = a_sequence-curve
# 
#     # pos
#     if(pos==1)
#     lines(a_sequence,b_sequence) # vertical
#     if(pos==2)
#     lines(b_sequence,a_sequence) # horizontal
# 
#     }

# brackets <- list(c("Overall", "Weight", "Weight"), 
#                  c("Engine", "Cylinders", "Horsepower"),
#                  c("Transmission", "Gears", "Manual"))
```

```{r}
args_m1g <- args_m %>% filter(depvar == "m1" & news == "good")
args_m1b <- args_m %>% filter(depvar == "m1" & news == "bad")
args_m3g <- args_m %>% filter(depvar == "m3" & news == "good")
args_m3b <- args_m %>% filter(depvar == "m3" & news == "bad")

if(!load_specification_matrices){
  system.time({mat1g <- specs_output(args_m1g)})
  mat1b <- specs_output(args_m1b)
  mat3g <- specs_output(args_m3g)
  mat3b <- specs_output(args_m3b)

save(mat1g, file = "data/temp/mat1g.Rda")
save(mat1b, file = "data/temp/mat1b.Rda")
save(mat3g, file = "data/temp/mat3g.Rda")
save(mat3b, file = "data/temp/mat3b.Rda")
}else{
load(file = "data/temp/mat1g.Rda")
load(file = "data/temp/mat1b.Rda")
load(file = "data/temp/mat3g.Rda")
load(file = "data/temp/mat3b.Rda")
}

```
```{r, echo=FALSE}
share_mat1g <- mean(mat1g$p<0.05) %>% round(digits = 3)
share_mat1b <- mean(mat1b$p<0.05) %>% round(digits = 3)
share_mat3g <- mean(mat3g$p<0.05) %>% round(digits = 3)
share_mat3b <- mean(mat3b$p<0.05) %>% round(digits = 3)

# #Vote choice: good news
# conds1g <- prep_graph(mat1g, args_m1g)
# prop.table(table(conds1g$categ[conds1g$sign_95 & conds1g$categ!= "ALL SPECIFICATIONS"])) %>% round(., 2) %>% sort
# #Vote choice: bad news
# conds1b <- prep_graph(mat1b, args_m1b)
# prop.table(table(conds1b$categ[conds1b$sign_95 & conds1b$categ!= "ALL SPECIFICATIONS"])) %>% round(., 2) %>% sort
# #Turnout: good news
# conds3g <- prep_graph(mat3g, args_m3g)
# prop.table(table(conds3g$categ[conds3g$sign_95 & conds3g$categ!= "ALL SPECIFICATIONS"])) %>% round(., 2) %>% sort
# #Turnout: bad news
# conds3b <- prep_graph(mat3b, args_m3b)
# prop.table(table(conds3b$categ[conds3b$sign_95 & conds3b$categ!= "ALL SPECIFICATIONS"])) %>% round(., 2) %>% sort
```

# What specifications matter most? 

The tables below show, for each row of specification choice C, the share of significant specifications when C = TRUE (sign_trues) and C = FALSE (sign_false) relative to the total share of unique *significant*  specifications.

The last column of the last row shows the total share of unique specifications that are significant (p < 0.05).

```{r}

share_sign_per_spec <- function(mat, args){
  # df <- as.data.frame(apply(args, 2, paste0), stringsAsFactors = FALSE)
  df <- args
  df$ate <- mat$ate
  df$p <- mat$p
  df$sign_95 <- (df$p < 0.05)
  df <- df %>% select(-depvar, -news, -ate, -p)
  
  # adjust coding for cov because not TRUE or FALSE
  df$cov <- (df$cov == "m14i+m17i+m18i+m20i+m21i+m22i+m24i+m26i+m27i")

  # percentage of significant specs occuring when choice = TRUE
  sign_trues <- sapply(1:ncol(df), function(c) sum(df$sign_95[df[,c] == TRUE])/sum(df$sign_95))
  # percentage of significant specs occuring when choice = FALSE
  sign_falses <- sapply(1:ncol(df), function(c) sum(df$sign_95[df[,c] == FALSE])/sum(df$sign_95))
  # share of total specifications where choice = TRUE
  share_true <- c(0, apply(df[,-1], 2, function(x) mean(x == TRUE)))

  # share_true["cov"] <- mean(df$cov)

  # adjust coding for ctry exclusion choice
  ctr <- c("ug1", "ug2", "bf", "brz", "mex", "ben", "none")
  for(i in 1:7){
    sign_trues[14+i] <- sum(df$sign_95[df[,1] == ctr[i]])/sum(df$sign_95) #nrow(df)
    sign_falses[14+i] <- sum(df$sign_95[df[,1] != ctr[i]])/sum(df$sign_95) #nrow(df)
    share_true[14+i] <- mean(df[,1] == ctr[i])
  }
  
  t <- as.data.frame(rbind(sign_trues, sign_falses, share_true))
  colnames(t) <- c(colnames(df), paste0("excl_", ctr))
  t <- round(t, 2) %>% t()
  t[c(1:13, 15:21, 14),]
}

#Vote choice: good news
t1 <- share_sign_per_spec(mat1g, args_m1g)
t1
#Vote choice: bad news
t2 <- share_sign_per_spec(mat1b, args_m1b)
t2
#Turnout: good news
t3 <- share_sign_per_spec(mat3g, args_m3g)
t3
#Turnout: bad news
t4 <- share_sign_per_spec(mat3b, args_m3b)
t4
```

```{r, echo=FALSE}

rnames <- c("Leave Out", "Burkina: recode M1", "Uganda 1: recode m10",
            "Mexico: recode m10", "Recode missing P", "Cluster: Level of politician", 
            "Weight studies equally", "Covariate adjusted", "Include Nij as covariate",
            "Uganda 2: include only contested seats", "Uganda 2: Exclude LCV councilors",
            "Uganda 2: Exclude redistricted councilors", 
            "Uganda 2: Exclude party switches",
            "Leave out: Uganda 1", "Leave out: Uganda 2", "Leave out: Burkina Faso",
            "Leave out: Brazil", "Leave out: Mexico", "Leave out: Benin", "Leave out: Include all",
            "Share of significant specifications")

format_tab <- function(tab, title, label, file){
  rownames(tab) <- rnames
  colnames(tab) <- c("TRUE" , "FALSE", "Share of TRUE (among all specifications)")
  print(xtable(tab[-1,], caption = title, label = label), header = FALSE,
        caption.placement = "top", file = file)
}

format_tab(t1, "Share of significant specifications by decision for vote choice (good news)",
            "tab:spec_m1g", "spec_m1g.tex")

format_tab(t2, "Share of significant specifications by decision for vote choice (bad news)",
            "tab:spec_m1b", "spec_m1b.tex")

format_tab(t3, "Share of significant specifications by decision for voter turnout (good news)",
            "tab:spec_m3g", "spec_m3g.tex")

format_tab(t4, "Share of significant specifications by decision for voter turnout (bad news)",
            "tab:spec_m3b", "spec_m3b.tex")


```


```{r, echo=FALSE}
cov <- "m14i+m17i+m18i+m20i+m21i+m22i+m24i+m26i+m27i"
atem1g <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = TRUE,
                    depvar = "m1", exclude_councilors = FALSE)$coefficients["treat",]
atem1b <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = TRUE,
                    depvar = "m1", exclude_councilors = FALSE)$coefficients["treat",]
atem3g <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = TRUE,
                    depvar = "m3", exclude_councilors = FALSE)$coefficients["treat",]
atem3b <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = TRUE,
                    depvar = "m3", exclude_councilors = FALSE)$coefficients["treat",]
```

# Vote for incumbent, good news

Percentage of specifications where $p$ < 0.05: `r toString(share_mat1g)`

```{r, echo=FALSE}
p1g <- plot_spec_ate(mat1g, args_m1g,
                     title = "Treatment effect of good news on vote for incumbent (meta-analysis)")

pdf("figures/fig_spec_curve_m1_good.pdf", height = 7, width = 12)
p1g
dev.off()

# g <- p1g %>% add_brackets(brackets)
# 
# pdf("figures/test.pdf", height = 7, width = 12)
# 
# grid.arrange(g)
# 
# dev.off()

if(export_to_book){
  pdf(paste0(book_dir, "/fig_spec_curve_m1_good.pdf"), height = 7, width = 12)
  p1g
  dev.off()
}

p1g
```

# Vote for incumbent, bad news

Percentage of specifications where $p$ < 0.05: `r toString(share_mat1b)`

```{r, echo=FALSE}
p1b <- plot_spec_ate(mat1b, args_m1b,
                     title = "Treatment effect of bad news on vote for incumbent (meta-analysis)")

pdf("figures/fig_spec_curve_m1_bad.pdf", height = 7, width = 12)
p1b
dev.off()

if(export_to_book){
  pdf(paste0(book_dir, "/fig_spec_curve_m1_bad.pdf"), height = 7, width = 12)
  p1b
  dev.off()
}

p1b
```

# Vote for incumbent, good and bad news

```{r, echo=FALSE}
# 
p1g <- plot_spec_ate(mat1g, args_m1g, title = "Treatment effect of information on vote for incumbent (meta-analysis)") + 
  labs(caption = "(a) Good news") +
  theme(plot.title = element_text(hjust = 0.5, size = 9),
        # plot.title = element_blank(),
        axis.text.y = element_text(size = 6),
        plot.caption=element_text(hjust=0.5, size = 9, margin=margin(2,0,1,0)),
        plot.margin = unit(c(1,2,.5,2), "cm"))+
  geom_vline(xintercept=atem1g, linetype="longdash")+
  coord_cartesian(xlim = c(min(c(mat1g$ate, mat1b$ate)), max(c(mat1g$ate, mat1b$ate)))) 

p1b <- plot_spec_ate(mat1b, args_m1b, title = "") +
  labs(caption = "(b) Bad news") +
  theme(plot.title = element_blank(),
        axis.text.y = element_text(size = 6),
        plot.caption=element_text(hjust=0.5, size = 9, margin=margin(2,0,1,0)),
        plot.margin = unit(c(0,2,1.5,2), "cm"))+
  geom_vline(xintercept=atem1b, linetype="longdash")+
  coord_cartesian(xlim = c(min(c(mat1g$ate, mat1b$ate)), max(c(mat1g$ate, mat1b$ate)))) 

pdf("figures/fig_spec_curve_m1.pdf")
grid.arrange(p1g, p1b, nrow = 2, widths = 8, heights = c(17, 16))
dev.off()

if(export_to_book){
  pdf(paste0(book_dir, "/fig_spec_curve_m1.pdf"))
  grid.arrange(p1g, p1b, nrow = 2, widths = 8, heights = c(17, 16))
  dev.off()
}
```

# Voter turnout, good news

Percentage of specifications where $p$ < 0.05: `r toString(share_mat3g)`

```{r, echo=FALSE}
pdf("figures/fig_spec_curve_m3_good.pdf", height = 7, width = 12)
plot_spec_ate(mat3g, args_m3g, title = "Treatment effect of good news on voter turnout (meta-analysis)")
dev.off()

if(export_to_book){
  pdf(paste0(book_dir, "/fig_spec_curve_m3_good.pdf"), height = 7, width = 12)
  plot_spec_ate(mat3g, args_m3g, title = "Treatment effect of good news on voter turnout (meta-analysis)")
dev.off()
}

  plot_spec_ate(mat3g, args_m3g, title = "Treatment effect of good news on voter turnout (meta-analysis)")

```

# Voter turnout, bad news

Percentage of specifications where $p$ < 0.05: `r toString(share_mat3b)`

```{r, echo=FALSE}
pdf("figures/fig_spec_curve_m3_bad.pdf", height = 7, width = 12)
plot_spec_ate(mat3b, args_m3b, title = "Treatment effect of bad news on voter turnout (meta-analysis)")
dev.off()

if(export_to_book){
  pdf(paste0(book_dir, "/fig_spec_curve_m3_bad.pdf"), height = 7, width = 12)
  plot_spec_ate(mat3b, args_m3b, title = "Treatment effect of bad news on voter turnout (meta-analysis)")
dev.off()
}

  plot_spec_ate(mat3b, args_m3b, title = "Treatment effect of bad news on voter turnout (meta-analysis)")

```

#Voter Turnout, good and bad news

```{r, echo=FALSE}
p3g <- plot_spec_ate(mat3g, args_m3g, title = "Treatment effect of information on voter turnout (meta-analysis)") + 
  labs(caption = "(a) Good news") +
  theme(plot.title = element_text(hjust = 0.5, size = 9),
        # plot.title = element_blank(),
        axis.text.y = element_text(size = 6),
        plot.caption=element_text(hjust=0.5, size = 9, margin=margin(2,0,1,0)),
        plot.margin = unit(c(1,2,.5,2), "cm")) +
  geom_vline(xintercept=atem3g, linetype="longdash") +
  coord_cartesian(xlim = c(min(c(mat3g$ate, mat3b$ate)), max(c(mat3g$ate, mat3b$ate)))) 

p3b <- plot_spec_ate(mat3b, args_m3b, title = "") +
  labs(caption = "(b) Bad news") +
  theme(plot.title = element_blank(),
        axis.text.y = element_text(size = 6),
        plot.caption=element_text(hjust=0.5, size = 9, margin=margin(2,0,1,0)),
        plot.margin = unit(c(0,2,1.5,2), "cm")) +
  geom_vline(xintercept=atem3b, linetype="longdash") +
  coord_cartesian(xlim = c(min(c(mat3g$ate, mat3b$ate)), max(c(mat3g$ate, mat3b$ate)))) 

pdf("figures/fig_spec_curve_m3.pdf")
grid.arrange(p3g, p3b, nrow = 2, widths = 8, heights = c(17, 16))
dev.off()

if(export_to_book){
  pdf(paste0(book_dir, "/fig_spec_curve_m3.pdf"))
  grid.arrange(p3g, p3b, nrow = 2, widths = 8, heights = c(17, 16))
  dev.off()
}
```

