---
title: "Code correct recollection"
author: "mk1"
date: "3/17/2018"
output: html_document
---

```{r, include=FALSE}
# Load clean data

# files <- list.files("data/temp", pattern = "covinter_clean", full.names = TRUE)
# for (f in files) {
#   load(f)
# }

```

# `correct`: dichotomous indicator for correct recall of Q

# Uganda 2
m30 is in the same scale as information given (`budget.actual`). "Don't know" answers are coded as 3 in line with Uganda 2 study.

```{r}
ug2$correct <- ifelse(ug2$m30==ug2$Q, 1,0)
ug2$post.prior.diff <- ug2$m30 - ug2$P
# ug2$post.prior.diff <- ifelse(ug2$N_good == 0, -ug2$post.prior.diff, ug2$post.prior.diff)
```

# Brazil:
m30 is already defined as whether posterior aligns with Q (information) (see 1a_prepdata.R). Difference between posterior and prior needs to be inverted so that positive differences means update toward better performance (m9-prior and m30 are both coded as 0 if account accepted and 1 if rejected).

```{r}
brz$correct <- brz$m30
brz$post.prior.diff <- brz$m9 - brz$m30 #inverted difference, see note above.
# brz$post.prior.diff <- ifelse(brz$N_good == 0, -brz$post.prior.diff, brz$post.prior.diff)
```

# Burkina
Recollection/attention check was administered to control only.

# Mexico:
Use existing m30 variable. The difference between posteriors and priors cannot be measured within subject due to lack of survey data administered pre-treatment.

```{r}
mexsur$correct <- mexsur$m30
```

# Benin
m30 scale (decreasing with quality) is inverted to match that of Q (increasing quality).
```{r}
ben$correct <- ifelse((5-ben$m30)==ben$Q,1,0)
ben$post.prior.diff <- (5-ben$m30) - ben$P
# ben$post.prior.diff <- ifelse(ben$N_good == 0, -ben$post.prior.diff, ben$post.prior.diff)
```

# Uganda 1
measure of m30 (SEE CONSTRUCTION OF MEASURE OF polknow_e BELOW) is substantively different from Q. See below. Difference between posteriors and priors here is coded directly from the measure of political knowledge (m30).

```{r}
# REVIEW
# STATA CODE
# *candsknown
# gen numcands_const = .
# replace numcands_const = 6 if code==18|code==16
# replace numcands_const = 5 if code==14
# replace numcands_const = 9 if code==19
# la var numcands_const "Number of candidates in constituency"
# 
# egen numcandsknown_e = total(heardofcand_e), by(id)
# tab numcandsknown_e
# replace numcandsknown_e = . if core==.
# la var numcandsknown_e "Number of candidates named by respondent, EL"
# gen sharecandsknown_e = numcandsknown_e / numcands_const
# tab sharecandsknown_e, mi
# la var sharecandsknown_e "Share of primary candidates known, EL"
# 
# gen sectorcorrectshr_e = numsectorcorrect_e / numcands_const
# la var sectorcorrectshr_e "Share of known cand priority sectors, EL"
# 
# *Melina: note that BL measure is not comparable to EL measure since we changed T/F questions at EL (no variation in most T/F)
# egen mpresp_e = rowtotal (correct1 correct2 correct3 correct4 correct5 correct6)
# la var  mpresp_e "Know: Roles of MPs, EL"
# replace mpresp_e = . if core== .
# tab mpresp_e
# drop correct1 - correct6
# 
# *Melina: Rescale such that variable is between 0 and 1. Min possible: -3. Max possible: +6
# gen mpresp_std_e = (mpresp_e - (-3)) / (6-(-3))
# tab mpresp_std_e 
# 
# *candsectorknow: Share of candidates for which a respondent can correctly name their priority sector. 
# tab sector_e
# tab priority_c
# destring priority_c, replace
# gen sectorcorrect_e = 0
# replace sectorcorrect_e = 1 if priority_c == sector_e
# replace sectorcorrect_e = . if priority_c == . | priority_c == .d | priority_c == .r | sector_e == . | sector_e == .d | sector_e == .r |sector_e==-88
# la var sectorcorrect_e "Knows candidate's priority sector, EL"
# 
# egen numsectorcorrect_e = total(sectorcorrect_e), by(id)
# replace numsectorcorrect_e = . if core_e == .
# 
# tab numsectorcorrect_e if uniqueid == 1
# la var numsectorcorrect_e "Number of cand priority sector correctly named by resp, EL"
# replace numsectorcorrect_e = . if core_e == .
# 
# gen sectorcorrectshr_e = numsectorcorrect_e / numcands_const
# la var sectorcorrectshr_e "Share of known cand priority sectors, EL"
#
# *Composite knowledge 
# gen polknow_e = sectorcorrectshr_e + mpresp_std_e + sharecandsknown_e
# tab polknow_e if uniqueid==1, mi
# la var polknow_e  "Political knowledge, EL"

# Generate dichotomous variable for correct recollection in Uganda
# for values above and below the mean of the political knowledge scale (1.5)
ug1$correct <- ifelse(ug1$m30 >= 1.5, 1, 0)
# ug1$post.prior.diff <- ug1$m30
save(ug1, file="data/temp/ug1_covinter_clean.Rda")

```

