---
title: "Replication code of Supplementary Information for 'Voter information campaigns and political accountability: Cumulative findings from a preregistered
meta-analysis of coordinated trials'"
date: February 22, 2019
output:
  pdf_document:
    fig_caption: yes
    fig_crop: yes
    toc: true # table of content true
    toc_depth: 3
    keep_tex: yes
    number_sections: yes
  word_document: default
header-includes:
- \usepackage{caption,tikz}
- \captionsetup{width=5in}
- \usepackage{graphicx}
abstract: ""
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}

rm(list = ls())

# packages

pks <- c("readstata13","reshape","dotwhisker", "MASS","plyr","dplyr","foreign",
         "tidyverse","lfe","stargazer","clubSandwich", "randomizr",
         "haven","rstudioapi", "stringr", "ri", "car", "xtable", "xlsx", "rmarkdown", "dplyr", 
         "iterators", "parallel")

invisible(lapply(pks, function(x) if (!require(x, character.only=T)){install.packages(x, repos = "http://cran.us.r-project.org");library(x, character.only = T)}))

# knitr options
require(knitr)
opts_knit$set(warning = FALSE, message = FALSE)
options(knitr.duplicate.label = 'allow')
options(xtable.comment = FALSE)

# create output folders
if(!"figures"%in%dir(file.path(getwd()))) dir.create(file.path(getwd(), "figures"))
if(!"tables"%in%dir(file.path(getwd()))) dir.create(file.path(getwd(), "tables"))
```

```{r, include=FALSE}
# SET REPLICATION OPTIONS
  # RI p-values could be generated from scratch, "generate", "load" from file, or "ignore"
  ri_action <- "generate"
  #number of RI permutations; 10 for trial runs; >2000 for real runs (slow)
  n_iter <- 2000
  # load existing permutation matrices for the RITE analysis
  load_iter_matrix <- TRUE
  # run bayesian analysis (requires Rstan installation)
  run_bayes <- FALSE
  # Code m1 = 0 for cases with m1 = NA and m3 = 0
  full_m1 <- TRUE
  #Show source code in compiled file
  show_code = FALSE
  #Compile PDF
  compile_pdf <- TRUE
```

```{r, include=F}
# load functions
source("0a_functions_main.R")
if(run_bayes) source("0b_functions_bayes.R")
```

```{r dataprep, echo = F, warning=F, message=F}

load("data/temp/madat.Rda")
load("data/temp/madat_iter.Rda")

# replaces N_good measure with alternative meaure of good news for Uganda1
# madat_iter$N_good[madat_iter$ctry=="ug1"] <- 1*(madat_iter$N_alt[madat_iter$ctry=="ug1"]>0)
```

# Table 2: Descriptive statistics for sample of good news

```{r, echo=FALSE, results="asis"}

  sum_tab <- madat %>% 
  select(ctry, treat, N, N_good, m1, m3, m5, m6, m8, m14, m15, m17, m18, m19, m20, m21, m22, m24, m26, m27) %>%
  # group_by(ctry) %>%
  # mutate_at(c("N","m5", "m6", "m8","m14", "m17", "m18", "m20", "m21", "m22", "m24", "m26", "m27"),
              # function(x) x - mean(x, na.rm = T)) %>%
  # ungroup() %>%
  as.data.frame() %>%
  reshape::rename(c(treat = "Treatment",
                    N = "Nij",
                    m1 = "Incumbent vote choice",
                    m3 = "Voter turnout",
                    m5 = "Effort", 
                    m6 = "Dishonesty", 
                    m8 = "Backlash", 
                    m14 = "Age", 
                    m15 = "Co-ethnicity", 
                    m17 = "Education", 
                    m18 = "Wealth", 
                    m19 = "Co-Partisanship", 
                    m20 = "Voted in past election", 
                    m21 = "Voted incumbent past election", 
                    m22 = "Clientelism", 
                    m23 = "Salience of information", 
                    m24 = "Credibility of information", 
                    m26 = "Secret ballot", 
                    m27 = "Free and fair elections"))

sum_tab_g <- sum_tab %>% subset(N_good == 1) %>% select(-N_good, -ctry) %>% 
  format_output(., title = "Descriptive statistics for sample of good news", omit.summary.stat = c("p25", "p75")) %>%
  {
  writeLines(., file("tables/tab_A11.1_sumstats_good.tex"))
  }

close(file("tables/tab_A11.1_sumstats_good.tex"))

sum_tab_b <- sum_tab %>% subset(N_good == 0) %>% select(-N_good, -ctry) %>% 
  format_output(.,title = "Descriptive statistics for sample of bad news", omit.summary.stat = c("p25", "p75")) %>%
  {
  writeLines(., file("tables/tab_A11.1_sumstats_bad.tex"))
  }
  
close(file("tables/tab_A11.1_sumstats_bad.tex"))

cat(readLines('tables/tab_A11.1_sumstats_good.tex'), sep = '\n')
```

# Table 3: Descriptive statistics for sample of bad news

```{r, results = "asis"}
cat(readLines('tables/tab_A11.1_sumstats_bad.tex'), sep = '\n')
```

\clearpage

# Table 4: Balance of covariates

```{r, echo=FALSE, warning=FALSE, message=FALSE}

madat$inv_wt <- NA
madat$inv_wt[madat$ctry == "brz"] <- madat$inv_wts[madat$ctry == "brz"]
madat$inv_wt[madat$ctry == "ug2"] <- madat$inv_wts2[madat$ctry == "ug2"]
madat$inv_wt[!madat$ctry %in% c("brz", "ug2") ] <- 1/.5 # assignment probability = .5 for all countries other than brazil and uganda 2

```

```{r, echo = FALSE, warning=FALSE, message=FALSE, results = 'asis'}
filename <- "tables/tab_A_balance_meta.tex"
balance_tab <- format_balance(make_balance_tab(madat))
writeLines(c(balance_tab[1], "\\caption{Balance of covariates}", balance_tab[2], 
               "\\footnotesize", balance_tab[3:length(balance_tab)]), file(filename)); close(file(filename))
cat(readLines(filename), sep = "\n")
```

\clearpage

# Figure 6: Power Analysis

```{r mde, include=F, eval=FALSE, cache=TRUE}
rmarkdown::render("fig_MDE_with_controls.Rmd")
```

```{r, out.width="\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Minimal detectable effects: Power analysis of minimal detectable effects, computed using Monte Carlo simulation. The horizontal axis varies the conjectured average treatment effect, while the vertical axis shows statistical power: the probability of rejecting the null hypothesis at $\\alpha=0.05$."), echo=FALSE, eval = FALSE}
  mde_plot(all_diagnoses[[1]], main = "(a) Vote for incumbent, good news")
  mde_plot(all_diagnoses[[2]], main = "(b) Vote for incumbent, bad news")
  mde_plot(all_diagnoses[[3]], main = "(c) Turnout, good news")
  mde_plot(all_diagnoses[[4]], main = "(d) Turnout, bad news")
```

```{r, include=FALSE}
  gc()
```

# Table 5: Effect of Information

```{r, echo=show_code, cache=TRUE}
# Treatment effects with nij and covariates
cov <- "m14i+m17i+m18i+m20i+m21i+m22i+m24i+m26i+m27i"

# vote choice
# good news
t1ncovc2 <- results(dat = madat_iter, sims = n_iter, ri_p = ri_action,
                    file_rite_obj = "data/temp/ri_m1pool_all_g_cov.Rda",
                    cov = cov, good = TRUE, with_N = TRUE, weights = TRUE, depvar = "m1", exclude_councilors = FALSE)
# bad news
t2ncovc2 <- results(dat = madat_iter, sims = n_iter, ri_p = ri_action,
                    file_rite_obj = "data/temp/ri_m1pool_all_b_cov.Rda",
                    cov = cov, good = FALSE, with_N = TRUE, weights = TRUE, depvar = "m1", exclude_councilors = FALSE)

# turnout
#good news
t3ncovc2 <- results(dat = madat_iter, sims = n_iter, ri_p = ri_action,
                    file_rite_obj = "data/temp/ri_m3pool_all_g_cov.Rda",
                    cov = cov, good = TRUE, with_N = TRUE, weights = TRUE, depvar = "m3", exclude_councilors = FALSE)
# bad news
t4ncovc2 <- results(dat = madat_iter, sims = n_iter, ri_p = ri_action, 
                    file_rite_obj = "data/temp/ri_m3pool_all_b_cov.Rda",
                    cov = cov, good = FALSE, with_N = TRUE, weights = TRUE, depvar = "m3", exclude_councilors = FALSE)

# vote choice overall
t_m1_o <- results(dat = madat_iter, sims = n_iter, ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_all_o_cov.Rda",
                  cov = cov, with_N = TRUE, depvar = "m1", exclude_councilors =FALSE)

# turnout overall
t_m3_o <- results(dat = madat_iter, sims = n_iter, ri_p = ri_action, file_rite_obj = "data/temp/ri_m3pool_all_o_cov.Rda",
                  cov = cov, with_N = TRUE, depvar = "m3", exclude_councilors =FALSE)

```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab1_main_effects.R")
  cat(readLines('tables/tab_11.1_main_effects.tex'), sep = '\n')
```
```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
  createt11.1("html")
```

\clearpage

# Table 7: Differential attrition

```{r, echo=FALSE, results= 'asis'}
get_attrition <- function(df = madat, y = "m1", country = NULL){
  meta <- TRUE
  if(!is.null(country)){df <- df[df$ctry == country,]; meta <- FALSE}
  df <- reweight(df, meta = meta)
  df$missing <- is.na(df[,y])
  
  mod <- felm(missing ~ treat|fe|0|cl, data = df, weights = df$wt)

  covs <- df %>% select(P, N_good, m13, m14, m15, m17, m18,
         m19, m20, m21, m22, m23, m24) %>% names()
  
  form <- paste0("missing ~ ",
               paste(paste0(covs, "*treat"), collapse = " + "),
               "|fe|0|cl") %>% as.formula()
  
  mod2 <- felm(form, data = df, weights = df$wt)
  f <- linearHypothesis(mod2, c("P:treat = 0", paste0("treat:", covs[-1], " = 0")))
  Fstat <- f$Chisq[2] %>% round(.,2)
  Pr_F <- f$`Pr(>Chisq)`[2] %>% round(.,2)
  table <- data.frame(est = mod$coefficients[1,1],
                    se = mod$se,
                    p = mod$pval)
  rownames(table) <- "Treatment"
  return(list(table = table,
              Fstat = Fstat,
              Pr_F = Pr_F))
}

r1 <- get_attrition()
missing_m1 <- r1$table %>% round(., 2)
missing_m1$se <- paste0("(", missing_m1$se, ")")

r3 <- get_attrition(y = "m3")
missing_m3 <- r3$table %>% round(., 2)
missing_m3$se <- paste0("(", missing_m3$se, ")")

missing <- cbind(missing_m1, missing_m3)
missing <- missing %>% xtable(caption = ) %>% capture.output()
# rownames(tab) <- c("All", "Benin", "Burkina Faso","Brazil","Mexico","Uganda 1", "Uganda 2")
missing[4] <- paste0(missing[6], "& \\multicolumn{3}{c}{Vote Choice}&\\multicolumn{3}{c}{Voter Turnout} \\\\")
missing[5] <- " & Estimate & Std. Error & $p$-value & Estimate & Std. Error & $p$-value \\\\ "
missing[11] <- missing[9]
missing[12] <- "\\begin{flushleft}\\textit{Note:} Table shows the effect size of treatment on data missingness in incumbent vote choice and voter turnout across the entire sample. Pr(F) shows the probability of rejecting the null that none of the covariates is differentally determining attrition across treatment and control conditions. All regressions include block fixed effects, standard errors clustered at the level of assingment and inverse propensity weights, and all countries are weighted equally.$^*$ $p<0.05$; $^{**}$ $p<0.01$; $^{***}$ $p<0.001$. \\end{flushleft}"
missing[13] <- missing[10]
missing[9] <- paste0("F-stat & \\multicolumn{3}{c}{", r1$Fstat , "}&\\multicolumn{3}{c}{", r3$Fstat, "} \\\\")
missing[10] <- paste0("Pr(F) & \\multicolumn{3}{c}{", r1$Pr_F , "}&\\multicolumn{3}{c}{", r3$Pr_F, "} \\\\ \\hline \\hline")

writeLines(c("\\begin{table}[h!]", "\\caption{Differential attrition}", missing[2:length(missing)]), file("tables/tab_A_attrition_meta.tex")); close(file("tables/tab_A_attrition_meta.tex"))
cat(readLines("tables/tab_A_attrition_meta.tex"), sep = "\n")
```

\clearpage

# Figure 7: Bayesian Meta-Analysis: Vote Choice

```{r, include=F, eval=run_bayes, cache=TRUE}
  library("rstan")
  rstan_options(auto_write = TRUE)
  options(mc.cores = parallel::detectCores())
```

```{r stan, warning=F, message=F, eval=FALSE}
# Stan code used in Fig 11.5 and 11.6 to sample from posterior distributions

  bmodel <- "
  data {
    int<lower=0> J; // number of countries 
    real y[J]; // estimated treatment effects
    real<lower=0> sigma[J]; // s.e. of effect estimates 
  }
  parameters {
    real mu; 
    real<lower=0> tau;
    real eta[J];
  }
  transformed parameters {
    real theta[J];
    for (j in 1:J)
      theta[j] = mu + tau * eta[j];
  }
  model {
    target += normal_lpdf(eta | 0, 1);
    target += normal_lpdf(y | theta, sigma);
  }
  "

```

```{r posterior_run, include=show_code, eval=run_bayes, cache=TRUE}
  
  # Function to make data from model
  take_results <- function(L) {
    out <- lapply(L, function(i)  coef(summary(i))[1,1:2])
    t(matrix(unlist(out),nrow = 2))
  }

  ### M1: Incumbent vote ###
  good_m1 <- take_results(lapply(list(t1c1, t1c2, t1c3, t1c4, t1c5, t1c6, t1c7), function(i) i$estimates))
  bad_m1 <- take_results(lapply(list(t2c1, t2c2, t2c3, t2c4, t2c5, t2c6, t2c7), function(i) i$estimates))

  ### M3: Turn out###
  good_m3 <- take_results(lapply(list(t3c1, t3c2, t3c3, t3c4, t3c5, t3c6, t3c7), function(i) i$estimates))
  bad_m3 <- take_results(lapply(list(t4c1, t4c2, t4c3, t4c4, t4c5, t4c6, t4c7), function(i) i$estimates))

```

```{r bayesfig1, include=F, cache=TRUE, eval=run_bayes}

  ### M1: Incumbent vote ###
  
  pdf("figures/fig_11.5_posteriors_incumbent.pdf", height = 7, width = 12)
  mar.default <- c(5,4,4,2) + 0.1
  par(mfrow = c(1,2),mar = mar.default + c(0, 2, 0, 0))
  bayes_result(my_data = good_m1, main = "Effects of Good News on Vote Choice")
  bayes_result(my_data = bad_m1,  main = "Effects of Bad News on Vote Choice")
  dev.off()
  
```

<!-- # ```{r, out.width="\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Bayesian Meta-analysis: Vote Choice. The solid dots and lines show the estimates from the Bayesian model; the top row shows the overall meta-estimate of $\\mu$ and $\\tau$. The white dots show the original frequentist estimates: in many cases shrinkage can be observed, especially in cases that have effects that are more imprecisely estimated."), echo=FALSE} -->
<!-- # bayes_result(my_data = good_m1, main = "Effects of Good News on Vote Choice") -->
<!-- # bayes_result(my_data = bad_m1,  main = "Effects of Bad News on Vote Choice") -->
<!-- # ``` -->
<!-- #  -->

<!-- ![](figures/fig_11.5_posteriors_incumbent.pdf){width=100%} -->

\clearpage

# Figure 8: Bayesian Meta-Analysis: Turnout

```{r bayesfig2, include=F, eval=run_bayes, cache=TRUE, message=FALSE, warning=FALSE}
  
  ### M3: Turn out###
  
  pdf("figures/fig_11.6_posteriors_turnout.pdf", height = 7, width = 12)
  mar.default <- c(5,4,4,2) + 0.1
  par(mfrow = c(1,2),mar = mar.default + c(0, 2, 0, 0)) 
  bayes_result(my_data = good_m3, main = "Effects of Good News on Turnout")
  bayes_result(my_data = bad_m3,  main = "Effects of Bad News on Turnout")
  dev.off()
  
```

```{r, out.width="\\linewidth", include=TRUE, fig.align="center", fig.cap=c("Bayesian Meta-analysis: Turnout. The solid dots and lines show the estimates from the Bayesian model; the top row shows the overall meta-estimate of $\\mu$ and $\\tau$. The white dots show the original frequentist estimates: in many cases shrinkage can be observed, especially in cases that have effects that are more imprecisely estimated."), echo=FALSE, eval=run_bayes}
  bayes_result(my_data = good_m3, main = "Effects of Good News on Turnout")
  bayes_result(my_data = bad_m3,  main = "Effects of Bad News on Turnout")
```

```{r, include=F, eval=run_bayes, cache=TRUE}
  rm(bayes_result, my_data)
  gc()
```

<!-- ![](figures/fig_11.6_posteriors_turnout.pdf) -->
\clearpage

# Table 11.3: Manipulation check (effect of treatment on correct recollection)

```{r vknowledge, echo=show_code, cache=T, eval=TRUE}
# source("1d_prep_manipulation.R")
madat_m30 <- madat %>% subset(!is.na(correct))

m30mc1_o <- estimates(dat = madat_m30, depvar = "correct", exclude_councilors = TRUE)
m30mc2_o <- estimates(dat = madat_m30, depvar = "correct", weights = FALSE, country = "ben")
m30mc3_o <- estimates(dat = madat_m30, depvar = "correct", country = "brz")
m30mc4_o <- estimates(dat = madat_m30, depvar = "correct", weights = FALSE, country = "mex")
m30mc5_o <- estimates(dat = madat_m30, depvar = "correct", weights = FALSE, country = "ug1")
m30mc6_o <- estimates(dat = madat_m30, depvar = "correct", weights = TRUE, country = "ug2", exclude_councilors = TRUE)
```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab2_mcheck.R")
  cat(readLines('tables/tab_11.2_mcheck.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
  createt11.2("html")
```

# Table 11.4: Manipulation check (difference between posteriors and priors)

```{r, echo=show_code}
madat_m30b <- madat %>% subset(!is.na(post.prior.diff))
madat_m30b$post.prior.diff <- abs(madat_m30b$post.prior.diff)

# overall news
m30mc1_g <- estimates(dat = madat_m30b, good = NULL, depvar = "post.prior.diff", exclude_councilors = TRUE)
m30mc2_g <- estimates(dat = madat_m30b, good = NULL, depvar = "post.prior.diff", weights = FALSE, country = "ben")
m30mc3_g <- estimates(dat = madat_m30b, good = NULL, depvar = "post.prior.diff", country = "brz")
# m30mc5_g <- estimates(dat = madat_m30b, good = TRUE, depvar = "post.prior.diff", weights = FALSE, country = "ug1")
m30mc6_g <- estimates(dat = madat_m30b, good = NULL, depvar = "post.prior.diff", weights = TRUE, country = "ug2", exclude_councilors = TRUE)
```

```{r gc52, include = FALSE, message=FALSE, warning=FALSE}
gc()
```

```{r, results = 'asis', echo=FALSE, include=compile_pdf}
source("code_formatting/tab2b_mcheck_postpriordiff.R")
cat(readLines('tables/tab_11.2_mcheck2.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.2_good(type = "html")
```

\clearpage

# Table 11.5: Effect of information on perception of importance of politician effort and honesty

```{r m5table, echo=show_code, cache=T}
# M5 ----
m5gc1 <- results(dat = madat_iter, good = TRUE, depvar = "m5", exclude_councilors = TRUE, sims = n_iter,
                 ri_p = ri_action, file_rite_obj = "data/temp/ri_m5pool_g_unadj.Rda")
## good news

m5bc1 <- results(dat = madat_iter, good = FALSE, depvar = "m5", exclude_councilors = TRUE, sims = n_iter,
                   ri_p = ri_action, file_rite_obj = "data/temp/ri_m5pool_b_unadj.Rda") ## bad news
# M6 ----
m6gc1 <- results(dat = madat_iter, good = TRUE, depvar = "m6", exclude_councilors = TRUE, sims = n_iter,
                   ri_p = ri_action, file_rite_obj = "data/temp/ri_m6pool_g_unadj.Rda")  ## good news

m6bc1 <- results(dat = madat_iter, good = FALSE, depvar = "m6", exclude_councilors = TRUE, sims = n_iter,
                   ri_p = ri_action, file_rite_obj = "data/temp/ri_m6pool_b_unadj.Rda") ## bad news

```

```{r, results='asis', include=compile_pdf, echo=FALSE}
  source("code_formatting/tab3_effort_honesty.R")
  cat(readLines('tables/tab_11.3_effort_honesty.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.3(type = "html")
```

\clearpage


# Table 11.6: Effect of information and source credibility on evaluation of politician effort and honesty

```{r m24table, echo = show_code, cache=T}
# Effort
m5_m24c1_g <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m5", interactvar = "m24", good = TRUE, 
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m5pool_m24_all_g_unadj.Rda")  ## good news

m5_m24c1_b <- results(dat = madat_iter, sims = n_iter,
                      depvar = "m5", interactvar = "m24", good = FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m5pool_m24_all_b_unadj.Rda") ## bad news

# Honesty
m6_m24c1_g <- results(dat = madat_iter, sims = n_iter,
                      depvar = "m6", interactvar = "m24", good = TRUE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m6pool_m24_all_g_unadj.Rda")  ## good news

m6_m24c1_b <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m6", interactvar = "m24", good = FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m6pool_m24_all_b_unadj.Rda")  ## bad news
```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab4_effort_honesty.R")
  cat(readLines('tables/tab_11.4_effort_honesty_credibility.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.4("html")
```

\clearpage

# Table 11.7: Relationship between evaluation of politician effort and honesty with vote choice

```{r t11.5, echo=show_code, cache=T, warning=FALSE}

madat_m1pool_g <- estimates(dat = madat_iter, weights = FALSE, depvar = "m1", return_df = TRUE, good = TRUE, exclude_councilors =FALSE) # good

  madat_m1pool_g <- madat_m1pool_g %>%
    group_by(ctry) %>%
    mutate(m5 = m5 - mean(m5, na.rm = T)) %>%
    mutate(m6 = m6 - mean(m6, na.rm = T)) %>%
    ungroup()

m1m5c1g <- felm(m1~m5|fe|0|cl, data = madat_m1pool_g) 
m1m6c1g <- felm(m1~m6|fe|0|cl, data = madat_m1pool_g) 

madat_m1pool_b <- estimates(dat = madat_iter, weights = FALSE, depvar = "m1", return_df = TRUE, good = FALSE, exclude_councilors =FALSE) # bad
  
madat_m1pool_b <- madat_m1pool_b %>%
    group_by(ctry) %>%
    mutate(m5 = m5 - mean(m5, na.rm = T)) %>%
    mutate(m6 = m6 - mean(m6, na.rm = T)) %>%
    ungroup()
    
m1m5c1b <- felm(m1~m5|fe|0|cl, data = madat_m1pool_b) 
m1m6c1b <- felm(m1~m6|fe|0|cl, data = madat_m1pool_b)
```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab5_m1_effort_honesty.R")
  cat(readLines('tables/tab_11.5_m1_effort_honesty.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.5("html")
```

\clearpage

<!-- ## Politician Response -->

# Table 11.8: Effect of bad news on politician backlash

```{r t11.6, echo=show_code, cache=T}
m8bc1 <- results(dat = madat_iter, good = FALSE, depvar = "m8",
                 ri_p = ri_action, file_rite_obj = "data/temp/ri_m8pool_all_b_unadj.Rda", sims = n_iter)

m8bc2 <- results(dat = madat_iter, good = FALSE, depvar = "m8", weights = FALSE, country = "ben",
                 ri_p = ri_action, file_rite_obj = "data/temp/ri_m8pool_ben_b_unadj.Rda", sims = n_iter)

m8bc3 <- results(dat = madat_iter, good = FALSE, depvar = "m8", weights = FALSE, country = "mex",
                 ri_p = ri_action, file_rite_obj = "data/temp/ri_m8pool_mex_b_unadj.Rda", sims = n_iter)

```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab6_backlash.R")
  cat(readLines('tables/tab_11.6_backlash.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.6("html")
rm(m8bc1, m8bc2, m8bc3)
```

\clearpage

# Table 15: Effect of moderators on incumbent vote choice

```{r coeth_table, echo=show_code, cache=T}
# Coethnicity
## Good news - Mean centred 
madat_m1_coethnic_mc_g <- prepdat_coethnic(madat_m1pool_g, madat_m1pool_g$m1, 0)
m1_m15mc_g1 <- results(dat = madat_m1_coethnic_mc_g, ri_p = ri_action,
                       file_rite_obj = "data/temp/ri_m1pool_m15_g_unadj.Rda",
                       depvar = "m1", interactvar = "m15", sims = n_iter, exclude_councilors = FALSE)

# Bad news - Mean centred
madat_m1_coethnic_mc_b <- prepdat_coethnic(madat_m1pool_b, madat_m1pool_b$m1, 0)
m1_m15mc_b1 <- results(dat = madat_m1_coethnic_mc_b, ri_p = ri_action, 
                       file_rite_obj = "data/temp/ri_m1pool_m15_b_unadj.Rda",
                       depvar = "m1", interactvar = "m15", sims = n_iter, exclude_councilors = FALSE)
```

```{r copart_table, echo=show_code, cache=T}
# Copartisan
## Good news - dichotomous 
madat_m1_copart_bin_g <- prepdat_copartisan(madat_m1pool_g, madat_m1pool_g$m1, 1)
m1_m19bin_g1 <- results(dat = madat_m1_copart_bin_g, ri_p = ri_action, 
                       file_rite_obj = "data/temp/ri_m1pool_m19_g_unadj.Rda",
                       depvar = "m1", interactvar = "m19", sims = n_iter, exclude_councilors = FALSE)
```

```{r,echo=show_code, cache=T}
## Bad news - dichotomous 
madat_m1_copart_bin_b <- prepdat_copartisan(madat_m1pool_b, madat_m1pool_b$m1, 1)
m1_m19bin_b1 <- results(dat = madat_m1_copart_bin_b, ri_p = ri_action, 
                        file_rite_obj = "data/temp/ri_m1pool_m19_b_unadj.Rda",
                       depvar = "m1", interactvar = "m19", sims = n_iter, exclude_councilors = FALSE)
```

```{r client_table, echo=show_code, cache=T}
# Clientelism
## Good news - Mean centred 
madat_m1_client_mc_g <- prepdat_client(madat_m1pool_g, madat_m1pool_g$m1, 0)
m1_m22mc_g1 <- results(dat = madat_m1_client_mc_g, ri_p = ri_action, 
                       file_rite_obj = "data/temp/ri_m1pool_m22_g_unadj.Rda",
                       depvar = "m1", interactvar = "m22", sims = n_iter, exclude_councilors = FALSE)
```

```{r mods, echo=show_code, cache=T}
## Bad news - Mean centred 
madat_m1_client_mc_b <- prepdat_client(madat_m1pool_b, madat_m1pool_b$m1, 0)
m1_m22mc_b1 <- results(dat = madat_m1_client_mc_b, ri_p = ri_action, 
                       file_rite_obj = "data/temp/ri_m1pool_m22_b_unadj.Rda",
                       depvar = "m1", interactvar = "m22", sims = n_iter, exclude_councilors = FALSE)
```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab7_moderators.R")
  cat(readLines('tables/tab_11.7_moderators.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.7("html")
rm(madat_m1_coethnic_mc_g, madat_m1_coethnic_mc_b, madat_m1_copart_bin_g,
   madat_m1_copart_bin_b, madat_m1_client_mc_g, madat_m1_client_mc_b)
```

\clearpage

# Table 16: Effect of information and context heterogenity on incumbent vote choice

```{r, echo=show_code, cache=T}
# M11 - certainty
m1_m11c1_g <- results(dat = madat_iter, sims = n_iter,
                      depvar = "m1", interactvar = "m11", good = TRUE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m11_all_g.Rda")  # good news

m1_m11c1_b <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m1", interactvar = "m11", good = FALSE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m11_all_b.Rda") # bad news
```

```{r, echo=show_code, cache=T}
# M26 - secret ballot
m1_m26c1_g <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m1", interactvar = "m26", good = TRUE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m26_all_g.Rda")  # good news
```

```{r, echo=show_code, cache=T}
m1_m26c1_b <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m1", interactvar = "m26", good = FALSE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m26_all_b.Rda") # bad news

```

```{r, echo=show_code, cache=T}
# M27 - free and fair election
m1_m27c1_g <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m1", interactvar = "m27", good = TRUE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m27_all_g.Rda")  # good news
```

```{r,echo=show_code, cache=T}
m1_m27c1_b <- results(dat = madat_iter, sims = n_iter, 
                      depvar = "m1", interactvar = "m27", good = FALSE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m27_all_b.Rda") # bad news
```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab8_context_hetero.R")
  cat(readLines('tables/tab_11.8_context_hetero.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.8("html")
```

\clearpage

# Table 17: Effect of information and electoral competition on vote choice


```{r, eval = T, echo=show_code, cache=T}
# low competition ----
# good news
madat_m1_m25lpool_g <- madat_m1pool_g %>%
	drop_na(m25) %>%
	filter(!ctry %in% c("bf","ug2")) %>%
	group_by(ctry) %>%
	filter(m25 <= median(m25)) %>%
	ungroup()

m1_m25lc1_g <- results(dat = madat_m1_m25lpool_g, sims = n_iter,
                       ri_p = ri_action, file_rite_obj = "data/temp/r1_m1pool_m25l_g.Rda",
                       good = TRUE, depvar = "m1")
rm(madat_m1_m25lpool_g)
```

```{r, echo=show_code, cache=T}
# bad news 
madat_m1_m25lpool_b <- madat_m1pool_b %>%
	drop_na(m25) %>%
	filter(!ctry %in% c("bf","ug2")) %>%
	group_by(ctry) %>%
	filter(m25 <= median(m25)) %>%
	ungroup()

m1_m25lc1_b <- results(dat = madat_m1_m25lpool_b, sims = n_iter,
                       ri_p = ri_action, file_rite_obj = "data/temp/r1_m1pool_m25l_b.Rda",
                       good = FALSE, depvar = "m1")
rm(madat_m1_m25lpool_b)

```

```{r, echo=show_code, cache=T}

# high competition ----
# good news
madat_m1_m25hpool_g <- madat_m1pool_g %>%
	drop_na(m25) %>%
	filter(!ctry %in% c("bf","ug2")) %>%
	group_by(ctry) %>%
	filter(m25 > median(m25)) %>%
	ungroup()

m1_m25hc1_g <- results(dat = madat_m1_m25hpool_g, sims = n_iter,
                       ri_p = ri_action, file_rite_obj = "data/temp/r1_m1pool_m25h_g.Rda",
                       good = TRUE, depvar = "m1", skip_prep = TRUE)
rm(madat_m1_m25hpool_g)
```

```{r, echo=show_code, cache=T}
# bad news regressions
madat_m1_m25hpool_b <- madat_m1pool_b %>%
	drop_na(m25) %>%
	filter(ctry!="bf"&ctry!="ug2") %>%
	group_by(ctry) %>%
	filter(m25 > median(m25)) %>%
	ungroup()


m1_m25hc1_b <- results(dat = madat_m1_m25hpool_b, sims = n_iter,
                       ri_p = ri_action, file_rite_obj = "data/temp/r1_m1pool_m25h_b.Rda",
                       good = FALSE, depvar = "m1", skip_prep = TRUE)
rm(madat_m1_m25hpool_b)
```

```{r, results='asis', echo=FALSE, include=compile_pdf}
  source("code_formatting/tab9_competition.R")
  cat(readLines('tables/tab_11.9_competition.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.9("html")
```

\clearpage

# Table 18: Effect of information and intervention-specific heterogenity on vote choice

```{r, eval = T, echo=show_code, cache=T}

t1nc1_g <- results(dat = madat_iter, sims = n_iter, depvar = "m1", good = TRUE, with_N = TRUE, exclude_councilors =FALSE,
                   ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_N_all_g.Rda")   #good news, nij

t1nc1_b <- results(dat = madat_iter, sims = n_iter, depvar = "m1", good = FALSE, with_N = TRUE, exclude_councilors =FALSE,
                   ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_N_all_b.Rda")  #bad news, nij
```
```{r, echo=show_code, cache=T}

# M24 - credibliity
m1_m24c1_g <- results(dat = madat_iter, sims = n_iter, depvar = "m1", interactvar = "m24", good = TRUE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m24_all_g.Rda") #good news

m1_m24c1_b <- results(dat = madat_iter, sims = n_iter, depvar = "m1", interactvar = "m24", good = FALSE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m24_all_b.Rda") #bad news
```
```{r, echo=show_code, cache=T}

# m23 - salience
m1_m23c1_g <- results(dat = madat_iter, sims = n_iter, depvar = "m1", interactvar = "m23", good = TRUE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m23_all_g.Rda")  #good news

m1_m23c1_b <- results(dat = madat_iter, sims = n_iter, depvar = "m1", interactvar = "m23", good = FALSE, exclude_councilors =FALSE,
                      ri_p = ri_action, file_rite_obj = "data/temp/ri_m1pool_m23_all_b.Rda") #bad news

```

```{r, results='asis', echo=FALSE, include=compile_pdf, warning=FALSE}
  source("code_formatting/tab10_intervention_hetero.R")
  cat(readLines('tables/tab_11.10_intervention_hetero.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.10(type = "html")
```

\clearpage

<!-- # Looking Forward: Does Public Information Boost
Informational Effects? -->


# Table 19: Interaction analysis: Effect of good news on incumbent vote choice

```{r, echo=F, results='asis', warning=FALSE}

  t1ncovc2 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = TRUE, depvar = "m1", exclude_councilors =FALSE)
  t1ncovc3 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "ben")
  t1ncovc4 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = TRUE, depvar = "m1", country = "brz")
  t1ncovc5 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "bf")
  t1ncovc6 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "mex")
  t1ncovc7 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "ug1")
  t1ncovc8 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = TRUE, depvar = "m1", country = "ug2")
  t1ncovc9 <- estimates(cov = cov, good = TRUE, with_N = TRUE, weights = TRUE, depvar = "m1", country = "ug2", exclude_councilors =FALSE)

  source("code_formatting/tab11_incumbent_interaction_good.R")
  gentab11()
  
  t11.11 <- capture.output(gentab11())
  
  fileConn <- file("tables/tab_11.11_interaction_incumbent_good.tex")
  writeLines(unlist(list("\\begin{table}[H]\\centering",
                         t11.11[3:4],
                         "\\scalebox{0.7}{",
                         t11.11[5:60],
                         "\\end{tabular}}",
                         "\\begin{flushleft} \\hspace{1cm} \\scriptsize{{\\textit{Note:}  The table presents results from fitting Equation \\ref{metaeq.main1a}. Standard errors are clustered at the level of treatment assignment. Results in columns (1) and (7) include vote choice for LCV councilors as well as chairs in the Uganda 2 study (see Buntaine et al., Chapter 8). This means each respondent in the Uganda 2 study enters twice, and we cluster the standard errors at the individual level. $^{*}$ $p<0.05$; $^{**}$ $p<0.01$; $^{***}$ $p<0.001$ }} \\end{flushleft} \\end{table}")), fileConn)
  close(fileConn)

```
\clearpage

# Table 20: Interaction analysis: Effect of bad news on incumbent vote choice

```{r, echo=F, results='asis', warning=FALSE}

  t2ncovc2 <- estimates(cov = cov, good = FALSE, with_N = TRUE, depvar = "m1", exclude_councilors =FALSE)
  t2ncovc3 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "ben")
  t2ncovc4 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = TRUE, depvar = "m1", country = "brz")
  t2ncovc5 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "bf")
  t2ncovc6 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "mex")
  t2ncovc7 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = FALSE, depvar = "m1", country = "ug1")
  t2ncovc8 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = TRUE, depvar = "m1", country = "ug2")
  t2ncovc9 <- estimates(cov = cov, good = FALSE, with_N = TRUE, weights = TRUE, depvar = "m1", country = "ug2", exclude_councilors =FALSE)

  source("code_formatting/tab12_incumbent_interaction_bad.R")
  gentab12()
  t11.12 <- capture.output(gentab12())
  
  fileConn <- file("tables/tab_11.12_interaction_incumbent_bad.tex")
  
  writeLines(unlist(list("\\begin{table}[H]\\centering",
                         t11.12[3:4],
                         "\\scalebox{0.7}{",
                         t11.12[5:60],
                         "\\end{tabular}}",
                         "\\begin{flushleft} \\hspace{1cm} \\scriptsize{{\\textit{Note:}  The table presents results from fitting Equation \\ref{metaeq.main1b}. Standard errors are clustered at the level of treatment assignment. Results in columns (1) and (7) include vote choice for LCV councilors as well as chairs in the Uganda 2 study (see Buntaine et al., Chapter 8). This means each respondent in the Uganda 2 study enters twice, and we cluster the standard errors at the individual level. $^{*}$ $p<0.05$; $^{**}$ $p<0.01$; $^{***}$ $p<0.001$ }} \\end{flushleft} \\end{table}")), fileConn)
  close(fileConn)
```
\clearpage

# Table 21: Private vs Public Information: Effect of good news on incumbent vote choice

```{r, echo=show_code, cache=T}

# Load and append data
files <- list.files("data/temp/pubpvt", pattern = "pp_covinter", full.names = TRUE)
for (f in files) {
  load(f)
}

madat <- rbind.fill(ben, mexsur, ug1)
madat$inv_wts <- NA
madat$inv_wts2 <- NA

m1c1_g <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = TRUE)
m1c2_g <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = TRUE, 
                  country = "ben", weights = FALSE)
m1c3_g <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = TRUE, 
                  country = "mex", weights = FALSE)
m1c4_g <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = TRUE, 
                  country = "ug1", weights = FALSE)
f_g <- f_equalcoeff(estimates(depvar = "m1", treat1and2 = TRUE, good = TRUE, return_df = TRUE), "m1")

m1c1_b <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = FALSE)
m1c2_b <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = FALSE, 
                  country = "ben", weights = FALSE)
m1c3_b <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = FALSE, 
                  country = "mex", weights = FALSE)
m1c4_b <- results(ri_p = "ignore", depvar = "m1", treat1and2 = TRUE, good = FALSE, 
                  country = "ug1", weights = FALSE)
f_b <- f_equalcoeff(estimates(depvar = "m1", treat1and2 = TRUE, good = TRUE, return_df = TRUE), "m1")

```

```{r, results='asis', echo=FALSE, include=compile_pdf, warning=FALSE}
  source("code_formatting/tab13_pvt_pub_good.R")
  cat(readLines('tables/tab_11.13_pvt_pub_good.tex'), sep = '\n')
```

```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.13("html")
```

\clearpage

# Table 22: Private vs Public Information: Effect of bad news on incumbent vote choice

```{r, echo=F, results='asis'}
  source("code_formatting/tab14_pvt_pub_bad.R")
  cat(readLines('tables/tab_11.14_pvt_pub_bad.tex'), sep = '\n')
```
```{r, results = 'asis', echo=FALSE, include=!compile_pdf}
print_t11.15("html")
```


